Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2015-01-12 main.tex
remove colors
new abstract

% Ajouts et progression
\def\modMF#1{\textcolor{teal}{#1}}
\def\moda#1{\textcolor{blue}{#1}}
% \def\modLP#1{\textcolor{magenta}{#1}}
% \def\modMM#1{\textcolor{blue}{#1}}
% \def\modOR#1{\textcolor{olive}{#1}}
%\def\modMF#1{#1} \def\moda#1{#1} \def\modLP#1{#1} \def\modMM#1{#1} \def\modOR#1{#1}

@@

\begin{abstract}
The Process Hitting is a recently introduced framework
designed for the modelling and analysis of concurrent systems.
The particular form of its actions (encoding the dynamics into the models)
allowed to define very efficient static analysis
based on local causality to compute reachability properties.
However, this modelling shows its limits when preemption features are needed,
and especially for cooperations
(that is, the regulation of two components that jointly interact with a third one).

In this paper, we focus on
the Asynchronous Automata Network (AAN) formalism,
which is an extension of the Process Hitting with an increased expressivity.
Like the Process Hitting,
the originality of AANs is the restrictions of the actions
that have an effect limited to exactly one component;
but unlike Process Hitting, their causality is not restricted to at most one other component.

We then develop a new refinement for the under-approximation of the static analysis
to efficiently compute results on the dynamics of AANs.
Because of the expressivity improvements,
this analysis gives more accurate results
than the previous works carried on the Process Hitting.
Furthermore, its complexity is still polynomial in the size of the model
and exponential in the number of possible “branchings” during the solving.

We also extend the applicability of this static analysis to
AANs with classes of priorities and to
Asynchronous Discrete Networks, either Boolean or multivalued,
which allows to efficiently study the dynamics of these widespread models
% efficiently under-approximate reachability properties
% in these widespread models.
We illustrate this on the model-checking of a signalling network of 94
components, which is unprecedented.
\end{abstract}
\begin{keyword}
discrete networks \sep
abstract interpretation \sep
reachability \sep
qualitative models \sep
systems biology
\end{keyword}
\end{frontmatter}

>>>>

% Ajouts et progression
\def\modMF#1{\textcolor{teal}{#1}}
\def\moda#1{\textcolor{blue}{#1}}
% \def\modLP#1{\textcolor{magenta}{#1}}
% \def\modMM#1{\textcolor{blue}{#1}}
% \def\modOR#1{\textcolor{olive}{#1}}
\def\modMF#1{#1} \def\moda#1{#1} \def\modLP#1{#1} \def\modMM#1{#1} \def\modOR#1{#1}

@@

\begin{abstract}
In this paper,
we develop a new refinement for an efficient under-approximation of the dynamics of
Asynchronous Automata Networks (AANs).
An AAN is an Automata Network with synchronous transitions between automata,
where each transition change the local state of exactly one automaton
(but any number of synchronizing local states are allowed).
The work we propose here
is based on static analysis by abstract interpretation,
which allows to prove that reaching a state with a given property
is possible,
without the same computational cost of usual model checkers.
Furthermore, its complexity is polynomial in the size of the model
and exponential in the number of possible “branchings” during the solving.

The under-approximation method presented in this paper is inspired
from the one developed specifically for the Process Hitting,
which is a sub-class of AANs.
Furthermore, we also introduce the notion of AANs with classes of priorities,
and show that they have the same expressivity as AANs without priorities,
thus extending the range of our under-approximation.
Finally, we illustrate our method on the model-checking of a signalling network
of 94 components, which is unprecedented.
\end{abstract}
\begin{keyword}
discrete networks \sep
abstract interpretation \sep
reachability \sep
qualitative models \sep
systems biology
\end{keyword}
\end{frontmatter}
